\Huge Conferences in the Era of Expensive Carbon

### 2019-06-23 main.tex
Nit

Ideally, at some point, governments will impose carbon pricing uniformly,
and all CO2e-intensive activities will have to pay it. But ACM can send a
strong message about the importance of this issue by acting now. In
particular, as several companies have shown, even an artificial ``internal
price'' on carbon creates a significant price signal that shapes behavior.
%
Thus, our second proposal is that {\bf ACM should impose a a surcharge on
  conferences based on their carbon footprint.}  The charge should be low at
the beginning and increase steadily (and predictably) year on year.
%
Conference organizers can then choose (on the basis of careful analysis of
data and weighing of benefits) how best to balance their budgets---whether
by decreasing per-participant emissions, decreasing (physical)
participation, increasing registration fees, soliciting additional corporate
sponsorship, or other, more creative, means.  \iflater\mwh{Problem: We
  showed just above that it's hard to figure out what to do. Come back to
  this point here and say that the surcharge will spur bold choices?  Maybe
  say that these choices won't necessarily be bad, but could be really
  great?}\fi

>>>>

Ideally, at some point, governments will impose carbon pricing uniformly,
and all CO2e-intensive activities will have to pay it. But ACM can send a
strong message about the importance of this issue by acting now. In
particular, as several companies have shown, even an artificial ``internal
price'' on carbon creates a significant price signal that shapes behavior.
%
Thus, our second proposal is that {\bf ACM should impose a surcharge on
  conferences based on their carbon footprint.}  The charge should be low at
the beginning and increase steadily (and predictably) year on year.
%
Conference organizers can then choose (on the basis of careful analysis of
data and weighing of benefits) how best to balance their budgets---whether
by decreasing per-participant emissions, decreasing (physical)
participation, increasing registration fees, soliciting additional corporate
sponsorship, or other, more creative, means.  \iflater\mwh{Problem: We
  showed just above that it's hard to figure out what to do. Come back to
  this point here and say that the surcharge will spur bold choices?  Maybe
  say that these choices won't necessarily be bad, but could be really
  great?}\fi
